CS6213 Project Report

### 2021-05-07 report/paper.tex
WIP

\subsection{Concolic Trace Generation}

>>>>

\subsection{Search Strategy for Trace Generation}

While the above techniques combined with TLC's standard breadth-first search were sufficient for traces of length around 22, two of the scenarios we were interested in (\texttt{CommitWhenConcurrentLeaders} and \texttt{MajorityOfClusterRestarts}) seemed not to have short traces, or in any case, traces that we could find our laptops before we gave up after 2 and a half hours of model checking time.

\begin{verbatim}
CommitWhenConcurrentLeaders == ~
    \E i, k \in DOMAIN history["global"] :
    /\ i < k
    /\ LET  x == history["global"][i]
            y == history["global"][k]
        IN
        /\ x.action = "BecomeLeader" /\ Cardinality(x.leaders) >= 2
        /\ y.action = "CommitEntry"
    \* Run for a few more steps
    /\ Len(history["global"]) >= k + 2
    \* Still have concurrent leaders
    /\ Cardinality(CurrentLeaders) >= 2
\end{verbatim}
